\thetitle

### 2021-03-03 writing/mutate-interesting.tex
adding new para abput itneresting scenarios

\item If the evaluation od a mutant module immediately raises an exception because
of the changes, there is no work for the rational programmer. Indeed, if the
stack trace contains source pointers to two modules, the scenario is still
uninteresting. Every ordinary benchmark program comes with a {\tt main} module
that acts as a driver, whose source is guaranteed to be included in the stack
trace.  Hence, the definition of interesting mutation insists on the presence of
three different modules in the stack trace. This guarantees that the debugging
scenario demands a sufficiently sophisticated effort, due to the interaction
between the buggy module with its context.  In these cases, the rational
programmer must examine at least two modules to locate the source of the faulty
interaction.

@@

>>>>

\item If the evaluation of a mutant module immediately raises an exception because
of the changes, there is no work for the rational programmer. Indeed, if the
stack trace contains source pointers to two modules, the scenario is still
uninteresting. Every ordinary benchmark program comes with a {\tt main} module
that acts as a driver, whose source is guaranteed to be included in the stack
trace.  Hence, the definition of interesting mutation insists on the presence of
three different modules in the stack trace. This guarantees that the debugging
scenario demands a sufficiently sophisticated effort, due to the interaction
between the buggy module with its context.  In these cases, the rational
programmer must examine at least two modules to locate the source of the faulty
interaction.

@@

The definition of interesting scenarios is more than a filter for
uninteresting mutants. It is also the guide for re-designing and refining
mutators until they collectively produce a sizable and diverse population of
interesting scenarios. For example, the {\tt wrap-cond} mutator casts the
tests of conditional expressions to the {\tt Any} type and, hence,
suppresses occurrence typing. However, an examination of the scenarios it
produces through the lens of the definition of interesting scenarios
reveals that none is interesting. The fully typed mutant does fails to
typecheck but its variant without type annotations never raises a run-time
error. In fact, it turns out 1/4 of the mutators originally designed for
the experiment fail to live up to the standard of the definition while
many of the rest of the mutators went thought rounds of tweaking
to increase their potency.
